MATD02 - Exploration of Finite Geometry

### 2024-10-20 paper/main.tex
chore: Get outline up for report, add some potential citations to look at fix: Revert scenes to an example to get them compiling

    \begin{abstract}
        This is where you write a brief paragraph summarizing the main idea of your topic and your approach. Keep it concise and clear, offering a high-level view of your paper.
    \end{abstract}

    \section{Introduction}
    Begin your report by introducing the topic. Clearly define the key concepts, notations, and theorems that will be discussed. Keep the language accessible to the entire MATD02 class.

    \section{Theorems and Proofs}

    \begin{theorem}
        State the first theorem here.
    \end{theorem}

    \begin{proof}
        Provide the proof for Theorem 1 here, step by step.
    \end{proof}

    \begin{theorem}
        State the second theorem here.
    \end{theorem}

    \begin{proof}
        Provide the proof for Theorem 2 here, ensuring clarity and logical flow.
    \end{proof}

    \section{Future Developments}
    In this section, discuss any potential future developments related to your topic. Mention related problems, extensions, or more advanced ideas, even if their proofs are not currently clear.

    \section{Conclusion}
    Summarize the key points covered in the report, including the theorems and their significance. Restate the main takeaways in a clear, concise manner.

@@

%\begin{document}
%    When you are not looking at it, this sentences stops citing~\cite{knuth1990}.
%
%    \bibliography{references}
%    \bibliographystyle{plain}
%\end{document}

>>>>

    \begin{abstract}
        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
        Pellentesque pretium ut neque ac lacinia.
        Aenean ultricies dapibus ultricies.
        Nam tristique posuere quam, eget varius lorem posuere a.
        Nam hendrerit magna ex, vehicula tempor quam maximus at.
        Lorem ipsum dolor sit amet, consectetur adipiscing elit.
        Nullam vitae ultrices nulla, at dapibus lectus.
        Nullam ultrices eros eu lorem laoreet elementum.
        Nullam ullamcorper in lectus vel varius.
        Praesent lobortis sem vitae elit posuere, in consectetur magna tempor.
        Vivamus nunc ligula, ullamcorper ac sapien vel, dignissim varius leo.
        Mauris vel suscipit metus, id ornare odio.
        Vivamus ultricies vehicula mi ut bibendum.
        Nullam sollicitudin elit sit amet velit lacinia, eget pretium nisl viverra.
        Nulla laoreet nisi non velit posuere, a vehicula diam vehicula.
        Donec fermentum commodo tortor, ac feugiat orci iaculis sit amet.
        Suspendisse luctus, velit eu placerat dapibus, justo felis mattis tortor, vitae blandit leo justo vitae nibh.
    \end{abstract}

    \section{Introduction}

    Introduce four/five point geometries as a way to start thinking about geometries more abstractly, use notes from\cite{sinn_course_2021}

    \section{The Fano plane}

    \begin{theorem}
        Ex. Each point is on exactly three lines
    \end{theorem}

    \begin{proof}

    \end{proof}

    \section{Connections to finite groups}
    Explore ideas in from the following sources\cite{carmichael_finite_1930,tsuzuku_finite_1982},
    I'd really like to look at broader connections than symmetry groups.

    \begin{theorem}
    \end{theorem}

    \begin{proof}
    \end{proof}

    \section{Future Developments}

    Take a look at notes from the group theory textbooks.

@@
